Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2022-01-22 analysis/paper/paper.Rmd
Updated sensitivity plot with values from Zimmerman et. al (1999)

# summarize potential Chinook eaten for each time period by one pikeminnow
impact_df = bio_results %>%
  group_by(season) %>%
  summarize(across(ends_with("_g"), max)) %>%
  pivot_longer(cols = ends_with("_g"),
               names_to = "perc_diet",
               values_to = "g_fish_cons") %>%
  mutate(across(perc_diet,
                str_extract,
                "[:digit:]+"),
         across(perc_diet,
                as.integer)) %>%
  crossing(p_chnk = c(.01, .10, .30, .50, .70, .90, 1)) %>%
  mutate(g_chnk = g_fish_cons * p_chnk) %>%
  mutate(n_chnk = ifelse(season == "Fall",
                         g_chnk / avg_DSR_g,
                         g_chnk / avg_NRR_g)) %>%
  left_join(spring_abund %>%
            select(N_F:Uci_F,
                   N_S:Uci_S) %>%
            pivot_longer(everything()) %>%
            mutate(season = if_else(str_detect(name, "_F$"),
                                    "Fall",
                                    "Spring")) %>%
            mutate(across(name,
                          str_remove,
                          "_F$"),
                    across(name,
                           str_remove,
                           "_S$")) %>%
            pivot_wider(names_from = name,
                        values_from = value)) %>%
  mutate(juv_N = N * n_chnk,
         juv_Lci = Lci * n_chnk,
         juv_Uci = Uci * n_chnk) %>%
  bind_cols(sar) %>%
  mutate(adult_N = juv_N * medsar,
         adult_Lci = juv_Lci * qnorm(0.025, medsar, sdsar),
         adult_Uci = juv_Uci * qnorm(0.975, medsar, sdsar))

@@

pos = position_dodge(width=0.3)
pm_est_labels <- c("Chapman","Schnabel","Schnabel \n Delayed-mixing")
all_est %>%

@@

impact_p = impact_df %>%
  select(season,
         perc_diet,
         p_chnk,
         N = juv_N,
         Lci = juv_Lci,
         Uci = juv_Uci) %>%
  group_by(perc_diet, p_chnk) %>%
  summarise(across(c("N", "Lci", "Uci"),sum),
            .groups = "drop") %>%
  mutate(Stage = "Juveniles") %>%
  mutate(p_chnk = p_chnk * 100) %>%
  rename(perc_chnk = p_chnk) %>%
  filter(perc_chnk %in% c(10, 30, 50)) %>%
  ggplot(aes(x = perc_diet,y = N, group=as.factor(perc_chnk), color=as.factor(perc_chnk))) +
  geom_point(size = 2) + geom_line(size = 1.05)+
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  scale_color_manual(name="Proportion Chinook", values=c("lightsteelblue","steelblue3","navyblue"))+
  theme(axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black"),
        legend.position = c(.15, .85),legend.background = element_blank(),
        legend.key.size = unit(.5, "cm"),legend.box = 'horizontal') +
  labs(y = "Estimated Chinook Consumed", x="Percent Fish in Pikeminnow Diet")

>>>>

# summarize potential Chinook eaten for each time period by one pikeminnow
impact_df = bio_results %>%
  group_by(season) %>%
  summarize(across(ends_with("_g"), max)) %>%
  pivot_longer(cols = ends_with("_g"),
               names_to = "perc_diet",
               values_to = "g_fish_cons") %>%
  mutate(across(perc_diet,
                str_extract,
                "[:digit:]+"),
         across(perc_diet,
                as.integer)) %>%
  crossing(p_chnk = c(.01, .10, .30, .50, .65, .90, 1)) %>%
  mutate(g_chnk = g_fish_cons * p_chnk) %>%
  mutate(n_chnk = ifelse(season == "Fall",
                         g_chnk / avg_DSR_g,
                         g_chnk / avg_NRR_g)) %>%
  left_join(spring_abund %>%
            select(N_F:Uci_F,
                   N_S:Uci_S) %>%
            pivot_longer(everything()) %>%
            mutate(season = if_else(str_detect(name, "_F$"),
                                    "Fall",
                                    "Spring")) %>%
            mutate(across(name,
                          str_remove,
                          "_F$"),
                    across(name,
                           str_remove,
                           "_S$")) %>%
            pivot_wider(names_from = name,
                        values_from = value)) %>%
  mutate(juv_N = N * n_chnk,
         juv_Lci = Lci * n_chnk,
         juv_Uci = Uci * n_chnk) %>%
  bind_cols(sar) %>%
  mutate(adult_N = juv_N * medsar,
         adult_Lci = juv_Lci * qnorm(0.025, medsar, sdsar),
         adult_Uci = juv_Uci * qnorm(0.975, medsar, sdsar))

@@

pos = position_dodge(width=0.3)
pm_est_labels <- c("Chapman","Schnabel","Schnabel \n [Delayed-mixing]")
all_est %>%

@@

impact_p = impact_df %>%
  select(season,
         perc_diet,
         p_chnk,
         N = juv_N,
         Lci = juv_Lci,
         Uci = juv_Uci) %>%
  group_by(perc_diet, p_chnk) %>%
  summarise(across(c("N", "Lci", "Uci"),sum),
            .groups = "drop") %>%
  mutate(Stage = "Juveniles") %>%
  mutate(p_chnk = p_chnk * 100) %>%
  rename(perc_chnk = p_chnk) %>%
  filter(perc_chnk %in% c(30, 50, 65)) %>%
  ggplot(aes(x = perc_diet,y = N, group=as.factor(perc_chnk), linetype=as.factor(perc_chnk))) +
  geom_line(size = 1.05)+
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  scale_linetype_manual(name="Percent juvenile chinook \nof total fish consumed", values=c("dotted","solid","dashed"))+
  theme(axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black"),
        legend.position = c(.19, .82),legend.background = element_blank(),
        legend.key.size = unit(.56, "cm"),legend.box = 'horizontal') +
  labs(y = "Estimated Chinook Consumed", x="Percent Fish in Pikeminnow Diet")
